\documentclass[11pt]{article}
\usepackage[gruvbox, fonts]{ahsansabit}

\usepackage[]{sansmathfonts}

\title{Checking for Basic Appearance}
\author{Civita}
\date{\today}


\begin{document}


\maketitle

How does the system look overall?
\aime{ Let's find how the package looks overall}

This package is a fork of the package \textsf{Ahsan}, so that it meets need of Physics Handouts and texts. 

Thing about Physics is, guys in IPHO did better than IMO, so it's a better chance to make such a fork. 

\pr{The problem is, we need to make a package that is kinda lighter and suits more to Physics and also use PdfLaTeX engine, also being hyperaesthetic and hypercustomizable, doable for entry level beginner.}

\solu{Start from something that's most closest similar package, \textsf{Ahsan}. Then rip off stuffs and put into it.}

But I had other things in mind.

\nt{This package is opensourced so do the fuck you want to do with it, but don't make monetary profit (\textbf{\textsf{GNU License}})}



We have added a room for doing, guess what, derivations!

\derive{
Cosine Law.
}{
Assume a triangle with sides $\vec{a}$, $\vec{b}$ and $\vec{c}$, so that,
\[ 
\vec{b}-\vec{a}=\vec{c}
\]
Now, if find $\vec{c}\cdot \vec{c}$,
\[ 
\vec{a}^2 + \vec{b}^2 - 2 \vec{a}\cdot \vec{b} \cos \theta
\]
Here $\theta$ is the angle between $\vec{a}$ and $\vec{b}$. So we get,
\[ 
    \boxed{ c^2 = a^2 + b^2 - 2 ab \cos \theta}
\]
}



The work is no where near done. I haven't worked enough on this. \textbf{Your job is to give me a feedback what should I put.}


\end{document}

